Parsing Postfix log files

### 2008-07-31 doc/logparser-results.tex
Removed the graphs showing breakdown of rule hits. Moved remaining graphs out of graphs section and removed graphs section. Minor corrections.

XXX EXPLAIN THE X-AXES ON THE GRAPHS\@.

@@

USE THE DATA COLLECTED ABOUT NUMBER OF RULES TRIED\@.  MAYBE INCLUDE IN
ORDERINGS SECTION\@?

@@

Parsing efficiency is an obvious concern when the parser routinely needs to
parse very large log files.  The server which generated the log files used
in testing this parser accepts approximately 10,000 mails for 700 users a
day; as expected there are far more mails received on weekdays than at
weekends.   Median log file size is 50MB, containing 285,000 log lines ---
large scale mail servers would have much larger log files.  Note that
\graphref{Mails received per day} and \tableref{Number of mails received
per day: statistics} show the number of mails received by \SMTP{} only; in
particular the mail loops noticeable in other graphs do not contribute to
these figures.

\showgraph{build/plot-mails-received}{Number of mails received per
day}{Mails received per day}

\showtable{build/mails-received-include-for-graph}{Number of mails received
per day}{Number of mails received per day: statistics}

@@

Parsing all \numberOFlogFILES{} log files in one run took
\input{build/timing-run-include.tex}.

The computer was dedicated to the task of gathering statistics from test
runs, and was not used for any other purpose while test runs were ongoing;
any services not necessary for running the tests were disabled.

@@

Full coverage of log lines is easy to achieve yet hard to maintain.  It is
easy to achieve full coverage for a limited set of log files (at the time
of writing the parser is tested with \numberOFrules{} rules, fully parsing
\numberOFlogFILES{} contiguous log files from Postfix 2.2 and 2.3), and new
rules are easy to add.  Maintaining full coverage is hard because other
servers have different restrictions with custom messages, \DNSBL{} messages
change over time, major releases of Postfix change warning messages
(usually adding more information), etc.,\ so over time the log lines drift
and change.  \Graphref{rule hits graph} shows the number of hits
for each rule over all \numberOFlogFILES{} log files; it is obvious that a
small number of rules match the vast majority of the lines, and more than
half the rules match fewer than 100 times.

@@

@@

\subsection{Graphs}

XXX FIGURE OUT WHERE TO PUT THESE GRAPHS\@; DO I NEED ALL THREE\@?

\showgraph{build/plot-action-distribution}{Distribution of rules per
action}{Distribution of rules per action}

The number of hits per rule is quite unevenly spread, resembling a Power
Law distribution~\cite{powerlaw}.

As \graphref{rule hits graph} is quite difficult to read it has been
separated into three sections: low, middle and high.

\showgraph{build/plot-hits-low}{Hits per rule (low)}{hits per rule low}

It is apparent from the low graph (\graphref{hits per rule low})
that some rules have few or no hits; those with zero hits are rules which
were written to parse log files used during development of the parser but
not utilised in the test runs performed for this document.

\showgraph{build/plot-hits-middle}{Hits per rule (middle)}{hits per rule
middle}

\showgraph{build/plot-hits-high}{Hits per rule (high)}{hits per rule
high}

\clearpage{}

>>>>

@@

XXX USE THE DATA COLLECTED ABOUT NUMBER OF RULES TRIED\@.  MAYBE INCLUDE IN
ORDERINGS SECTION\@?

@@

Parsing efficiency is an obvious concern when the parser routinely needs to
parse very large log files.  The server which generated the log files used
in testing this parser accepts approximately 10,000 mails for 700 users a
day; \graphref{Mails received per day} shows that as expected there are far
more mails received on weekdays than at weekends.   Median log file size is
50MB, containing 285,000 log lines --- large scale mail servers would have
much larger log files.  Note that \graphref{Mails received per day} and
\tableref{Number of mails received per day: statistics} show the number of
mails received by \SMTP{} only; in particular the mail loops noticeable in
other graphs do not contribute to these figures.

\showgraph{build/plot-mails-received}{Number of mails received via SMTP per
day}{Mails received per day}

\showtable{build/mails-received-include-for-graph}{Number of mails received
via SMTP per day}{Number of mails received per day: statistics}

@@

Parsing all \numberOFlogFILES{} log files in one run took
\input{build/timing-run-include.tex}.  The computer was dedicated to the
task of gathering statistics from test runs, and was not used for any other
purpose while test runs were ongoing; any services not necessary for
running the tests were disabled.

@@

Full coverage of log lines is easy to achieve yet hard to maintain.  It is
easy to achieve full coverage for a limited set of log files (at the time
of writing the parser is tested with \numberOFrules{} rules, fully parsing
\numberOFlogFILESall{} contiguous log files from Postfix 2.2 through to
Postfix 2.5), and new rules are easy to add.  Maintaining full coverage is
hard because other servers have different restrictions with custom
messages, \DNSBL{} messages change over time, major releases of Postfix
change warning messages (usually adding more information), etc.,\ so over
time the log lines drift and change.  \Graphref{rule hits graph} shows the
number of hits for each rule over all \numberOFlogFILES{} log files.  The
number of hits per rule is quite unevenly spread, resembling a Power Law
distribution~\cite{powerlaw} --- it is obvious that a small number of rules
match the vast majority of the lines, and more than half the rules match
fewer than 100 times.

@@

\subsection{Summary}

XXX EXTEND TO SUMMARISE PARSER EFFICIENCY TOO\@.

XXX REWRITE COVERAGE SUMARY IF NECESSARY\@.

@@
